---
title: "Seasonality in Spatial Synchrony"
author: "Jonathan Walter"
date: "8 October 2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

setwd("~/GitHub/synchrony-seasonality")
```

## Overview

This R Markdown document organizes for completeness and replicability a series of simulations examining how seasonality in the degree of environmental spatial synchrony affects population spatial synchrony and metapopulation variability

# Comparison between analytical solution and simulations

First, compare analytical solution to an equivalent simulation model to confirm it works

```{r analytical.compare, echo=FALSE, cache=TRUE}
# library(parallel)
# library(lhs)
library(rootSolve)
source("~/GitHub/synchrony-seasonality/simmod_main.R")

## start with one example, then move to a search over the parameter space
tmax = 1000
burn = 100
f0 = 1.1
kB = 20
s0 = -0.5
kW = 20
cor.ebij = 0.6
cor.ewij = 0.5
cor.ebew = 0.5
sd.e = 0.01
dfrac = 0

  
analytical.solution<-function(f0, kB, s0, kW, cor.ebij, cor.ewij, cor.ebew, sd.e){
  
  #find equilibrium value of N; this is when rate = 0
  rate <- function(N){
    exp(f0)*exp(-N/kB) * exp(s0)*exp(-(N*exp(f0)*exp(-N/kB))/kW) - 1
  }
  
  Eq <- uniroot.all(rate, c(1, max(c(kB,kW))*1.5))
  
  #test stability of equilibrium
  eig <- vector()
  for (i in 1:length(Eq)){
    eig[i] <- sign (gradient(rate, Eq[i]))
  }
  
  if(!any(eig==-1)){
    stop("No stable equilibria between N=1 and N=1.5*max(kB, kW)")
  }
  
  Neq <- Eq[eig==-1] #take the stable equilibrium if multiple
  
  
  # #compute derivatives at N
  g <- expression(Neq*exp(f0)*exp(-Neq/kB)*exp(eB)*exp(s0)*exp(-(Neq*exp(f0)*exp(-Neq/kB)*exp(eB))/kW)*exp(eW))
  dgdeb <- D(g, 'eB')
  dgdew <- D(g, 'eW')
  eB <- eW <- 0
  PB <- as.numeric(eval(dgdeb))
  PW <- as.numeric(eval(dgdew))
  
  #convert between correlation/sd and covariance/variance
  cov.ebij <- cor.ebij*(sd.e^2)
  cov.ewij <- cor.ewij*(sd.e^2)
  cov.ebew <- cor.ebew*(sd.e^2)
  var.e <- sd.e^2
  
  # this is equation 26 from Dan's math document
  return((PB^2*cov.ebij + PW^2*cov.ewij + 2*PB*PW*cov.ebew)/(PB^2*var.e + PW^2*var.e + 2*PB*PW*cov.ebew))
  
}

linear.test<-simmod_main(tmax, f0, kB, s0, kW, cor.ebij, cor.ewij, cor.ebew, sd.e, dfrac, getBt=TRUE)

#plot(linear.test$Nt[,1])

#cor(linear.test$Nt[-c(1:burn),])
#cor(linear.test$Bt[-c(1:burn),], use="pairwise.complete.obs")
#cor(linear.test$env[-c(1:burn),])


#plot(linear.test$Nt[,1])

analytical.solution(f0, kB, s0, kW, cor.ebij, cor.ewij, cor.ebew, sd.e)

cor(linear.test$Nt[-c(1:burn),])

```

Next, independently and simultaneously vary environmental correlation while holding other factors constant
```{r analytical.surface, echo=FALSE, cache=TRUE}

a2=0.5
rho.b=seq(0,1,by=0.01)
rho.w=rho.b
sd.b=0.5
sd.w=sd.b
nlocs=2

analytical.solution2<-function(a2, rho.b, rho.w, sd.b, sd.w){ #assumes that cov(eb1,ew2) = 0 & cov(ew1,eb2) = 0

  ax = (1 - a2)
  var.b = sd.b^2
  var.w = sd.w^2
  
  return((ax^2*(rho.b*var.b) + (rho.w*var.w))/(ax^2*var.b + var.w))
}
  
varrhos.analytical1<-matrix(NA, length(rho.b), length(rho.w))
for(ii in 1:length(rho.b)){
  for(jj in 1:length(rho.w)){
    varrhos.analytical1[ii,jj]<-analytical.solution2(a2, rho.b[ii], rho.w[jj], sd.b, sd.w)
  }
}

#vary a2 while holding spatial synchrony and driver variance constant
a2seq<-seq(0,1,by=0.05)

a2_v1.analytical<-rep(NA, length(a2seq))
a2_v2.analytical<-rep(NA, length(a2seq))
a2_v3.analytical<-rep(NA, length(a2seq))

for(ii in 1:length(a2seq)){
  
  a2_v1.analytical[ii]<-analytical.solution2(a2seq[ii], rho.b=0.7, rho.w=0.3, sd.b, sd.w)
  a2_v2.analytical[ii]<-analytical.solution2(a2seq[ii], rho.b=0.3, rho.w=0.7, sd.b, sd.w)
  a2_v3.analytical[ii]<-analytical.solution2(a2seq[ii], rho.b=0.5, rho.w=0.5, sd.b, sd.w)
  
}


## change driver variances while pinning synchrony and a2 <------------------------------------------------------------
sd.bseq<-seq(0,1,0.05)
sd.wseq<-seq(0,1,0.05)

sd.b_v1.analytical<-rep(NA, length(sd.bseq))
sd.w_v1.analytical<-rep(NA, length(sd.wseq))

sd.b_v2.analytical<-rep(NA, length(sd.bseq))
sd.w_v2.analytical<-rep(NA, length(sd.wseq))

sd.b_v3.analytical<-rep(NA, length(sd.bseq))
sd.w_v3.analytical<-rep(NA, length(sd.wseq))

for(ii in 1:length(sd.bseq)){
  
  sd.b_v1.analytical[ii]<-analytical.solution2(a2, rho.b=0.3, rho.w=0.7, sd.b=sd.bseq[ii], sd.w=sd.w)
  sd.w_v1.analytical[ii]<-analytical.solution2(a2, rho.b=0.3, rho.w=0.7, sd.b=sd.b, sd.w=sd.wseq[ii])
  
  sd.b_v2.analytical[ii]<-analytical.solution2(a2, rho.b=0.7, rho.w=0.3, sd.b=sd.bseq[ii], sd.w=sd.w)
  sd.w_v2.analytical[ii]<-analytical.solution2(a2, rho.b=0.7, rho.w=0.3, sd.b=sd.b, sd.w=sd.wseq[ii])
  
  sd.b_v3.analytical[ii]<-analytical.solution2(a2, rho.b=0.5, rho.w=0.5, sd.b=sd.bseq[ii], sd.w=sd.w)
  sd.w_v3.analytical[ii]<-analytical.solution2(a2, rho.b=0.5, rho.w=0.5, sd.b=sd.b, sd.w=sd.wseq[ii])
  
}

pal<-colorRampPalette(colors=c("red","white","blue"))


#Make nice figure!
png("~/GitHub/synchrony-seasonality/fig1_analytical.png", units="in", res=300, width=3, height=8)

par(mfrow=c(3,1), mar=c(3.5,3.5,1.5,1), mgp=c(1.7,0.5,0))
#varying synchrony
image(rho.b, rho.w, varrhos.analytical1, zlim=c(-1,1), col=pal(50),
      xlab=expression(rho[b]), ylab=expression(rho[w]))
contour(rho.b, rho.w, varrhos.analytical1, add=T)
mtext(expression(paste(a[2]," = 0.5, var(",epsilon[b],") = var(",epsilon[w],") = 0.25")), cex=0.6)

#varying a2
plot(a2seq, a2_v1.analytical, type="l", ylim=c(0,1), xlab=expression(a[2]), ylab="Population synchrony")
lines(a2seq, a2_v2.analytical, lty=2)
lines(a2seq, a2_v3.analytical, lty=3)
mtext(expression(paste("var(",epsilon[b],") = var(",epsilon[w],") = 0.25")), cex=0.6)
legend("topright", legend=c(expression(paste(rho[b]," = 0.3, ",rho[w]," = 0.7")), 
                            expression(paste(rho[b]," =  ",rho[w]," = 0.5")), 
                            expression(paste(rho[b]," = 0.7, ",rho[w]," = 0.3"))), 
       lty=c(1,3,2), bty="n", cex=0.9)

#varying driver variances
plot(sd.bseq, sd.b_v1.analytical, type="l", ylim=c(0,1), xlab="Driver variance",
     ylab="Population synchrony")
lines(sd.wseq, sd.w_v1.analytical, lty=1, col="red")

lines(sd.bseq, sd.b_v2.analytical, lty=2)
lines(sd.wseq, sd.w_v2.analytical, lty=2, col="red")

lines(sd.bseq, sd.b_v3.analytical, lty=1)
lines(sd.wseq, sd.w_v3.analytical, lty=3, col="red")
mtext(expression(paste(a[2]," = 0.5")), cex=0.6)
legend("top", ncol=2, legend=c(expression(paste("changing var(",epsilon[b],")"))
                               , expression(paste("changing var(",epsilon[w],")"))), 
       lty=1, col=c("black","red"), bty="n", cex=0.9)
legend("bottom", ncol=2, legend=c(expression(paste(rho[b]," = 0.3, ",rho[w]," = 0.7")), 
                            expression(paste(rho[b]," = ",rho[w]," = 0.5")), 
                            expression(paste(rho[b]," = 0.7, ",rho[w]," = 0.3"))), 
       lty=c(1,3,2), bty="n", cex=0.9)

dev.off()

```


# Effects of seasonality on synchrony and extinction, nonlinear dynamics 

Model is based on Ricker-style density dependence

```{r sim.sensitivity, echo=FALSE, cache=TRUE}
rm(list=ls())
library(parallel)
library(lhs)
library(dplyr)
source("simmod_main.R")
source("simmod_alt_nowinter.R")
source("simmod_alt_sameenv.R")
nn<-200

# 
# set.seed(666)
# hypercube<-optimumLHS(n=nn, k=9)
# saveRDS(hypercube, "hypercube.rds")
hypercube <- readRDS("hypercube.rds")

f0=qunif(hypercube[,1],0.3,2.45)
kB=qunif(hypercube[,2],10,200)
s0=qunif(hypercube[,3],-0.9, 0)*f0
kW=kB*qunif(hypercube[,4],0.1,1)
cor.ebij=qunif(hypercube[,5],0,1)
cor.ewij=qunif(hypercube[,6],0,1)
sd.e=hypercube[,7]
dfrac=qunif(hypercube[,8],0,0.2)
cor.ebew=qunif(hypercube[,9],-0.5,0.5)
cor.eij <- cor.ebij

tmax=10000
burn=1000

ncores=detectCores()-4

cl<-makeCluster(ncores)
main.sample<-mcmapply(simmod_main, tmax, f0, kB, s0, kW, cor.ebij, cor.ewij, cor.ebew,
                      sd.e, dfrac, getBt=TRUE, SIMPLIFY=FALSE)

nowint.sample<-mcmapply(simmod_nowinter, tmax, f0, kB, cor.ebij, cor.ewij, cor.ebew,
                        sd.e, dfrac, getBt=TRUE, SIMPLIFY=FALSE)

sameenv.sample<-mcmapply(simmod_sameenv, tmax, f0, kB, s0, kW, cor.eij, sd.e, dfrac, 
                         getBt=TRUE, SIMPLIFY=FALSE)

stopCluster(cl)

#helper function for getting cor(Nt)
getNtcor<-function(inlist){ #extract synchrony in Nt
  out<-rep(NA, length(inlist))
  for(ii in 1:length(inlist)){
    tmp<-inlist[[ii]]$Nt[-c(1:burn),]
    out[ii]<-cor(tmp)[2,1]
  }
  return(out)
}


for(ii in 1:length(main.sample)){
  
  tmp <- main.sample[[ii]]$Nt
  plot(tmp[-c(1:burn),1], type="l", main=paste(ii))
  lines(tmp[-c(1:burn),2], col="blue")
  
}

  
#make data frames for analysis  
sampres.main <- data.frame(rhoN=getNtcor(main.sample), 
                          #scale predictors to standardize effect sizes
                       f0=scale(f0), kB=scale(kB), s0=scale(s0), kW=scale(hypercube[,4]), cor.ebij=scale(cor.ebij),
                       cor.ewij=scale(cor.ewij), sd.e=scale(sd.e), dfrac=scale(dfrac))

sampres.nowint <- data.frame(rhoN=getNtcor(nowint.sample), 
                          #scale predictors to standardize effect sizes
                       f0=scale(f0), kB=scale(kB), cor.ebij=scale(cor.ebij),
                       cor.ewij=scale(cor.ewij), sd.e=scale(sd.e), dfrac=scale(dfrac))

sampres.sameenv <- data.frame(rhoN=getNtcor(sameenv.sample), 
                          #scale predictors to standardize effect sizes
                       f0=scale(f0), kB=scale(kB), s0=scale(s0), kW=scale(hypercube[,4]), cor.ebij=scale(cor.eij),
                       sd.e=scale(sd.e), dfrac=scale(dfrac))

#regression analysis
lm.main.rhoN<-lm(rhoN ~ f0 + kB + s0 + kW + cor.ebij + cor.ewij + cor.ebew + sd.e + dfrac + 
                   cor.ebij:cor.ewij + kB:kW + f0:cor.ebij + s0:cor.ewij, 
                 data=sampres.main, na.action=na.exclude)
summary(lm.main.rhoN)
#hist(resid(lm.main.rhoN))
modsumm.main<-summary(lm.main.rhoN)

lm.nowint.rhoN<-lm(rhoN ~ f0 + kB + cor.ebij + cor.ewij + sd.e + dfrac + cor.ebew +
                     cor.ebij:cor.ewij + f0:cor.ebij, 
                 data=sampres.nowint, na.action=na.exclude)
summary(lm.nowint.rhoN)
#hist(resid(lm.nowint.rhoN))
modsumm.nowint<-summary(lm.nowint.rhoN)

lm.sameenv.rhoN<-lm(rhoN ~ f0 + kB + s0 + kW + cor.ebij + sd.e + dfrac +
                      kB:kW + f0:cor.ebij + s0:cor.ebij, 
                 data=sampres.main, na.action=na.exclude)
summary(lm.sameenv.rhoN)
hist(resid(lm.sameenv.rhoN))
modsumm.sameenv<-summary(lm.sameenv.rhoN)

#compile results into a figure
effects.main <- modsumm.main$coefficients[-1,1]
effects.main <- as.data.frame(effects.main)
effects.main$param <- row.names(effects.main)

effects.sameenv <- modsumm.sameenv$coefficients[-1,1]
effects.sameenv <- as.data.frame(effects.sameenv)
effects.sameenv$param <- row.names(effects.sameenv)

effects.nowint <- modsumm.nowint$coefficients[-1,1]
effects.nowint <- as.data.frame(effects.nowint)
effects.nowint$param <- row.names(effects.nowint)

effects.comb <- left_join(effects.main, effects.sameenv)
effects.comb <- left_join(effects.comb, effects.nowint)

saveRDS(effects.comb, file="~/GitHub/synchrony-seasonality/sim_sensitivity.RDS")

barplot(t(as.matrix(effects.comb[,-2])), beside=T, names.arg=effects.comb$param,
        legend.text=c("main", "same environment", "no overwintering"),
        args.legend=list(x="topleft",bty="n"), las=2)

```


```{r runModels_varsynch1, echo=FALSE, cache=TRUE}
library(parallel)
source("simmod_main.R")
source("simmod_alt_nowinter.R")
source("simmod_alt_sameenv.R")

scentxt<-"set1"

#parameter set 1
rho<-seq(0,1,by=0.05)

tmax = 2000
burn = 1000
f0 = 1.8
kB = 100
s0 = -0.1
kW = 80
cor.ebij = rep(expand.grid(rho,rho)[,1],each=10)
cor.ewij = rep(expand.grid(rho,rho)[,2],each=10)
cor.ebew = 0
sd.e = 0.1
dfrac = 0
cor.eij = cor.ebij



ncores=detectCores()-4

cl<-makeCluster(ncores)

main.varrhos<-mcmapply(simmod_main, tmax, f0, kB, s0, kW, cor.ebij, cor.ewij, cor.ebew,
                      sd.e, dfrac, getBt=TRUE, SIMPLIFY=FALSE)
nowint.varrhos<-mcmapply(simmod_nowinter, tmax, f0, kB, cor.ebij, cor.ewij, cor.ebew,
                        sd.e, dfrac, getBt=TRUE, SIMPLIFY=FALSE)
sameenv.varrhos<-mcmapply(simmod_sameenv, tmax, f0, kB, s0, kW, cor.eij, sd.e, dfrac, 
                         getBt=TRUE, SIMPLIFY=FALSE)

stopCluster(cl)


#helper function for getting cor(Nt)
getNtcor<-function(inlist){ #extract synchrony in Nt
  out<-rep(NA, length(inlist))
  for(ii in 1:length(inlist)){
    tmp<-inlist[[ii]]$Nt[-c(1:burn),]
    out[ii]<-cor(tmp)[2,1]
  }
  return(out)
}

#helper function for getting cor(NB)
getNtcor<-function(inlist){ #extract synchrony in Nt
  out<-rep(NA, length(inlist))
  for(ii in 1:length(inlist)){
    tmp<-inlist[[ii]]$Bt[-c(1:burn),]
    out[ii]<-cor(tmp)[2,1]
  }
  return(out)
}


# Ntcor.df<-data.frame(rho.b=rho.b, rho.w=rho.w, Ntcor=getNtcor(varrhos.ddall))
# Ntcor.agg<-aggregate(Ntcor.df, by=list(rho.b, rho.w), FUN=mean, na.rm=T)
# Ntcor.mat<-matrix(Ntcor.agg$Ntcor, nrow=length(rho), ncol=length(rho))
# 
# Btcor.df<-data.frame(rho.b=rho.b, rho.w=rho.w, Btcor=getBtcor(varrhos.ddall))
# Btcor.agg<-aggregate(Btcor.df, by=list(rho.b, rho.w), FUN=mean, na.rm=T)
# Btcor.mat<-matrix(Btcor.agg$Btcor, nrow=length(rho), ncol=length(rho))
# 
# Ntcor.df.br<-data.frame(rho.b=rho.b, rho.w=rho.w, Ntcor=getNtcor(varrhos.basic))
# Ntcor.agg.br<-aggregate(Ntcor.df.br, by=list(rho.b, rho.w), FUN=mean, na.rm=T)
# Ntcor.mat.br<-matrix(Ntcor.agg.br$Ntcor, nrow=length(rho), ncol=length(rho))
# 

# 
# 
# diff2.Ntcor<-Ntcor.mat-Ntcor.mat.br
# diff2.El<-El.mat-El.mat.br
# diff2.Eg<-Eg.mat-Eg.mat.br
# 
# diff.NtBtcor<-Ntcor.mat-Btcor.mat
# 
# pal<-colorRampPalette(colors=c("red","white","blue"))
# 
# 
# ## Make figure comparing syncrhony in different seasons
# 
# png(paste0("~/GitHub/synchrony-seasonality/fig3_compare_seasons.png"), units="in", res=300, width=6.1, height=2.3)
# 
# par(mfrow=c(1,3), mar=c(1.8,1.8,1.5,0), mgp=c(2.7,0.5,0), tcl=-0.3, oma=c(1.1,1,0,1))
# image(rho, rho, Ntcor.mat, xlab="", ylab="", asp=1, main="cor(Nt)",
#       col=pal(50), zlim=c(-1,1))
# contour(rho, rho, Ntcor.mat, add=T)
# text(0.05,0.95,"a)")
# 
# image(rho, rho, Btcor.mat, xlab="", ylab="", asp=1, main="cor(Bt)",
#       col=pal(50), zlim=c(-1,1))
# contour(rho, rho, Btcor.mat, add=T)
# text(0.05,0.95,"b)")
# 
# image(rho, rho, diff.NtBtcor, xlab="", ylab="", asp=1, main="cor(Nt)-cor(Bt)",
#       col=pal(50), zlim=c(-.6,.6))
# contour(rho, rho, diff.NtBtcor, add=T)
# text(0.05,0.95,"c)")
# 
# mtext("Spatial synchrony of breeding season environment",1,outer=T,cex=0.8)
# mtext("Overwintering synchrony",2,outer=T,cex=0.8)
# 
# dev.off()
# 
# 
# 
# #make figure comparing main model to alternate
# 
# png(paste0("~/GitHub/synchrony-seasonality/fig4_compare_alternates",scentxt,".png"), units="in", res=300, width=6, height=6.55)
# 
# par(mfcol=c(3,3), mar=c(2,2,2.5,1), oma=c(1.5,1.5,0,0),mgp=c(2,0.6,0), tcl=-0.4)
# #main model
# image(rho, rho, Ntcor.mat, xlab="", ylab="", asp=1, 
#       main="", col=pal(50), zlim=c(-1,1))
# tmpdf<-data.frame(z=c(Ntcor.mat), x=expand.grid(rho,rho)[,1], y=expand.grid(rho,rho)[,2])
# sm<-matrix(predict(loess(z~x+y, data=tmpdf, span=0.1)),length(rho),length(rho))
# contour(rho, rho, sm, add=T)
# mtext("Main model",3,line=0.1,cex=0.7)
# text(0.05,0.95,"a)")
# 
# image(rho, rho, El.mat, xlab="", ylab="", asp=1, 
#       main="", col=pal(50), zlim=c(-.1,.1))
# tmpdf<-data.frame(z=c(El.mat), x=expand.grid(rho,rho)[,1], y=expand.grid(rho,rho)[,2])
# sm<-matrix(predict(loess(z~x+y, data=tmpdf, span=0.1)),length(rho),length(rho))
# contour(rho, rho, sm, add=T, levels=c(0.07,0.09,0.11,0.13))
# mtext("Main model",3,line=0.1, cex=0.7)
# text(0.05,0.95,"d)")
# 
# image(rho, rho, Eg.mat, xlab="", ylab="", asp=1, 
#       main="",
#       col=pal(50), zlim=c(-.015,.015))
# tmpdf<-data.frame(z=c(Eg.mat), x=expand.grid(rho,rho)[,1], y=expand.grid(rho,rho)[,2])
# sm<-matrix(predict(loess(z~x+y, data=tmpdf, span=0.1)),length(rho),length(rho))
# contour(rho, rho, sm, add=T, levels=c(0.001,0.003,0.005,0.007,0.009,0.011))
# mtext("Main model",3,line=0.1, cex=0.7)
# text(0.05,0.95,"g)")
# 
# #difference - basic ricker
# image(rho, rho, diff2.Ntcor, xlab="", ylab="", asp=1, main="",
#       col=pal(50), zlim=c(-.3,.3))
# tmpdf<-data.frame(z=c(diff2.Ntcor), x=expand.grid(rho,rho)[,1], y=expand.grid(rho,rho)[,2])
# sm<-matrix(predict(loess(z~x+y, data=tmpdf, span=0.1)),length(rho),length(rho))
# contour(rho, rho, sm, add=T)
# mtext("Difference: alternate 1",3,line=0.1,cex=0.7)
# mtext("Population spatial synchrony",3,line=1.1,cex=0.9)
# text(0.05,0.95,"b)")
# 
# image(rho, rho, diff2.El, xlab="", ylab="", asp=1, main="",
#       col=pal(50), zlim=c(-.15,.15))
# tmpdf<-data.frame(z=c(diff2.El), x=expand.grid(rho,rho)[,1], y=expand.grid(rho,rho)[,2])
# sm<-matrix(predict(loess(z~x+y, data=tmpdf, span=0.1)),length(rho),length(rho))
# contour(rho, rho, sm, add=T, levels=c(-0.04,-0.02,0,0.02,0.04,0.06))
# mtext("Difference: alternate 1",3,line=0.1,cex=0.7)
# mtext("Local extinction rate",3,line=1.1,cex=0.9)
# text(0.05,0.95,"e)")
# 
# image(rho, rho, diff2.Eg, xlab="", ylab="", asp=1, main="",
#       col=pal(50), zlim=c(-.015,.015))
# tmpdf<-data.frame(z=c(diff2.Eg), x=expand.grid(rho,rho)[,1], y=expand.grid(rho,rho)[,2])
# sm<-matrix(predict(loess(z~x+y, data=tmpdf, span=0.1)),length(rho),length(rho))
# contour(rho, rho, sm, add=T, levels=c(-0.003,-0.002,-0.001,0,0.001,0.002,0.003))
# mtext("Difference: alternate 1",3,line=0.1,cex=0.7)
# mtext("Global extinction rate",3,line=1.1,cex=0.9)
# text(0.05,0.95,"h)")
# 
# #difference - alternate seasonal model
# image(rho, rho, diff.Ntcor, xlab="", ylab="", asp=1, main="",
#       col=pal(50), zlim=c(-.3,.3))
# tmpdf<-data.frame(z=c(diff.Ntcor), x=expand.grid(rho,rho)[,1], y=expand.grid(rho,rho)[,2])
# sm<-matrix(predict(loess(z~x+y, data=tmpdf, span=0.1)),length(rho),length(rho))
# contour(rho, rho, sm, add=T)
# mtext("Difference: alternate 2",3,line=0.1,cex=0.7)
# text(0.05,0.95,"c)")
# 
# image(rho, rho, diff.El, xlab="", ylab="", asp=1, main="",
#       col=pal(50), zlim=c(-.15,.15))
# tmpdf<-data.frame(z=c(diff.El), x=expand.grid(rho,rho)[,1], y=expand.grid(rho,rho)[,2])
# sm<-matrix(predict(loess(z~x+y, data=tmpdf, span=0.1)),length(rho),length(rho))
# contour(rho, rho, sm, add=T, levels=c(-0.1,-0.08,-0.06,-0.04,-0.02,0))
# mtext("Difference: alternate 2",3,line=0.1,cex=0.7)
# text(0.05,0.95,"f)")
# 
# image(rho, rho, diff.Eg, xlab="", ylab="", asp=1, main="",
#       col=pal(50), zlim=c(-.015,.015))
# tmpdf<-data.frame(z=c(diff.Eg), x=expand.grid(rho,rho)[,1], y=expand.grid(rho,rho)[,2])
# sm<-matrix(predict(loess(z~x+y, data=tmpdf, span=0.1)),length(rho),length(rho))
# contour(rho, rho, sm, add=T, levels=c(-0.009,-0.007,-0.005,-0.003,-0.002,-0.001,0))
# mtext("Difference: alternate 2",3,line=0.1,cex=0.7)
# text(0.05,0.95,"i)")
# 
# mtext("Spatial synchrony of breeding season environment",1,outer=T,cex=0.9)
# mtext("Spatial synchrony of overwintering season environment",2,outer=T,cex=0.9)
# 
# dev.off()
# 


```


```{r ddall.varrhos.multnoise, echo=FALSE, cache=F}
library(parallel)
source("~/GitHub/synchrony-seasonality/Fn_synchmod_dd_multnoise_202102102.R")
source("~/GitHub/synchrony-seasonality/Fn_synchmod_dd_alt_multnoise_20210210.R")
source("~/GitHub/synchrony-seasonality/Fn_synchmod_basicricker_multnoise_20181016.R")

scentxt<-"r08Db0Kb10"

rho<-seq(0,1,by=0.05)
rho.b<-rep(expand.grid(rho,rho)[,1],each=100)
rho.w<-rep(expand.grid(rho,rho)[,2],each=100)
r=0.8
Kb=10
Kw=Kb
sd.b=0.2
sd.w=0.2
Db=0
Dw=0
nlocs=2
tmax=550

ncores=detectCores()-4

cl<-makeCluster(ncores)
varrhos.ddall<-mcmapply(synchmod_dd_multnoise,r=r,Kb=Kb,Kw=Kw,rho.b=rho.b,rho.w=rho.w,
                        sd.b=sd.b,sd.w=sd.w,Db=Db,tmax=tmax,nlocs=nlocs, SIMPLIFY = F)
varrhos.alt<-mcmapply(synchmod_dd_alt_multnoise,r=r,Kb=Kb,Kw=Kw,rho.b=rho.b,rho.w=rho.w,
                        sd.b=sd.b,sd.w=sd.w,Db=Db,tmax=tmax,nlocs=nlocs, SIMPLIFY = F)
varrhos.basic<-mcmapply(synchmod_basicricker_multnoise,r=r,K=Kb,rho.b=rho.b,rho.w=rho.w,
                        sd.b=sd.b,sd.w=sd.w,Db=Db,tmax=tmax,nlocs=nlocs, SIMPLIFY = F)

stopCluster(cl)


getNtcor<-function(inlist){ #extract synchrony in Nt
  out<-rep(NA, length(inlist))
  for(ii in 1:length(inlist)){
    tmp<-log(inlist[[ii]]$Nt[,-c(1:50)]+1)
    tmprho<-cor(t(tmp), use = "pairwise.complete.obs")
    out[ii]<-mean(tmprho[lower.tri(tmprho)])
  }
  return(out)
}

getBtcor<-function(inlist){ #extract synchrony in Nt
  out<-rep(NA, length(inlist))
  for(ii in 1:length(inlist)){
    tmp<-log(inlist[[ii]]$Bt[,-c(1:50)]+1)
    tmprho<-cor(t(tmp), use = "pairwise.complete.obs")
    out[ii]<-mean(tmprho[lower.tri(tmprho)])
  }
  return(out)
}

getEl<-function(inlist){ #extract local extinction rate
  out<-rep(NA, length(inlist))
  for(ii in 1:length(inlist)){
    tmp<-inlist[[ii]]$Nt[,-c(1:50)]
    out[ii]<-sum(tmp==0,na.rm=T)/sum(!is.na(tmp))
  }
  return(out)
}

getEg<-function(inlist){ #extract global extinction rate
  out<-rep(NA, length(inlist))
  for(ii in 1:length(inlist)){
    tmp<-inlist[[ii]]$Nt[,-c(1:50)]
    if(all(is.na(tmp))){out[ii]<-NA}
    else if(sum(colSums(tmp)==0, na.rm=T)==0){out[ii]<-0}
    else{out[ii]<-1/(which(colSums(tmp)==0)+50)}
  }
  return(out)
}

Ntcor.df<-data.frame(rho.b=rho.b, rho.w=rho.w, Ntcor=getNtcor(varrhos.ddall))
Ntcor.agg<-aggregate(Ntcor.df, by=list(rho.b, rho.w), FUN=mean, na.rm=T)
Ntcor.mat<-matrix(Ntcor.agg$Ntcor, nrow=length(rho), ncol=length(rho))

Btcor.df<-data.frame(rho.b=rho.b, rho.w=rho.w, Btcor=getBtcor(varrhos.ddall))
Btcor.agg<-aggregate(Btcor.df, by=list(rho.b, rho.w), FUN=mean, na.rm=T)
Btcor.mat<-matrix(Btcor.agg$Btcor, nrow=length(rho), ncol=length(rho))

Ntcor.df.alt<-data.frame(rho.b=rho.b, rho.w=rho.w, Ntcor=getNtcor(varrhos.alt))
Ntcor.agg.alt<-aggregate(Ntcor.df.alt, by=list(rho.b, rho.w), FUN=mean, na.rm=T)
Ntcor.mat.alt<-matrix(Ntcor.agg.alt$Ntcor, nrow=length(rho), ncol=length(rho))

Ntcor.df.br<-data.frame(rho.b=rho.b, rho.w=rho.w, Ntcor=getNtcor(varrhos.basic))
Ntcor.agg.br<-aggregate(Ntcor.df.br, by=list(rho.b, rho.w), FUN=mean, na.rm=T)
Ntcor.mat.br<-matrix(Ntcor.agg.br$Ntcor, nrow=length(rho), ncol=length(rho))

El.df<-data.frame(rho.b=rho.b, rho.w=rho.w, El=getEl(varrhos.ddall))
El.agg<-aggregate(El.df, by=list(rho.b, rho.w), FUN=mean, na.rm=T)
El.mat<-matrix(El.agg$El, nrow=length(rho), ncol=length(rho))

El.df.alt<-data.frame(rho.b=rho.b, rho.w=rho.w, El=getEl(varrhos.alt))
El.agg.alt<-aggregate(El.df.alt, by=list(rho.b, rho.w), FUN=mean, na.rm=T)
El.mat.alt<-matrix(El.agg.alt$El, nrow=length(rho), ncol=length(rho))

El.df.br<-data.frame(rho.b=rho.b, rho.w=rho.w, El=getEl(varrhos.basic))
El.agg.br<-aggregate(El.df.br, by=list(rho.b, rho.w), FUN=mean, na.rm=T)
El.mat.br<-matrix(El.agg.br$El, nrow=length(rho), ncol=length(rho))

Eg.df<-data.frame(rho.b=rho.b, rho.w=rho.w, Eg=getEg(varrhos.ddall))
Eg.agg<-aggregate(Eg.df, by=list(rho.b, rho.w), FUN=mean, na.rm=T)
Eg.mat<-matrix(Eg.agg$Eg, nrow=length(rho), ncol=length(rho))

Eg.df.alt<-data.frame(rho.b=rho.b, rho.w=rho.w, Eg=getEg(varrhos.alt))
Eg.agg.alt<-aggregate(Eg.df.alt, by=list(rho.b, rho.w), FUN=mean, na.rm=T)
Eg.mat.alt<-matrix(Eg.agg.alt$Eg, nrow=length(rho), ncol=length(rho))

Eg.df.br<-data.frame(rho.b=rho.b, rho.w=rho.w, Eg=getEg(varrhos.basic))
Eg.agg.br<-aggregate(Eg.df.br, by=list(rho.b, rho.w), FUN=mean, na.rm=T)
Eg.mat.br<-matrix(Eg.agg.br$Eg, nrow=length(rho), ncol=length(rho))

#avg.mat<-matrix(rowMeans(expand.grid(rho,rho)), nrow=length(rho), ncol=length(rho))
diff.Ntcor<-Ntcor.mat-Ntcor.mat.alt
diff.El<-El.mat-El.mat.alt
diff.Eg<-Eg.mat-Eg.mat.alt

diff2.Ntcor<-Ntcor.mat-Ntcor.mat.br
diff2.El<-El.mat-El.mat.br
diff2.Eg<-Eg.mat-Eg.mat.br

diff.NtBtcor<-Ntcor.mat-Btcor.mat

pal<-colorRampPalette(colors=c("red","white","blue"))

# tiff(paste0("~/Box Sync/SynchronyLifestageModel/plotoutput/compare_rho_main_multnoise",scentxt,".tif"), units="in", res=300, width=6.5, height=2.2)
# 
# par(mfrow=c(1,3), mar=c(4,4,1.5,1), mgp=c(2.7,1,0), tcl=-0.4)
# image(rho, rho, Ntcor.mat, xlab="Breeding synchrony", ylab="Overwintering synchrony", asp=1, main="cor(Nt)",
#       col=pal(50), zlim=c(-1,1))
# contour(rho, rho, Ntcor.mat, add=T)
# 
# image(rho, rho, Btcor.mat, xlab="Breeding synchrony", ylab="Overwintering synchrony", asp=1, main="cor(Bt)",
#       col=pal(50), zlim=c(-1,1))
# 
# contour(rho, rho, Btcor.mat, add=T)
# 
# image(rho, rho, diff.NtBtcor, xlab="Breeding synchrony", ylab="Overwintering synchrony", asp=1, main="cor(Nt)-cor(Bt)",
#       col=pal(50), zlim=c(-.35,.35))
# contour(rho, rho, diff.NtBtcor, add=T)
# 
# dev.off()
# 
# 
# tiff(paste0("~/Box Sync/SynchronyLifestageModel/plotoutput/compare_vs_alt_multnoise",scentxt,".tif"), units="in", res=300, width=6.5, height=6.5)
# 
# par(mfcol=c(3,3), mar=c(4,4,1.5,1), mgp=c(2.7,1,0), tcl=-0.4)
# #main model
# image(rho, rho, Ntcor.mat, xlab="Breeding synchrony", ylab="Overwintering synchrony", asp=1, main="main cor(Nt)",
#       col=pal(50), zlim=c(-1,1))
# tmpdf<-data.frame(z=c(Ntcor.mat), x=expand.grid(rho,rho)[,1], y=expand.grid(rho,rho)[,2])
# sm<-matrix(predict(loess(z~x+y, data=tmpdf, span=0.1)),length(rho),length(rho))
# contour(rho, rho, sm, add=T)
# 
# image(rho, rho, El.mat, xlab="Breeding synchrony", ylab="Overwintering synchrony", asp=1, main="main El",
#       col=pal(50), zlim=c(-.11,.11))
# tmpdf<-data.frame(z=c(El.mat), x=expand.grid(rho,rho)[,1], y=expand.grid(rho,rho)[,2])
# sm<-matrix(predict(loess(z~x+y, data=tmpdf, span=0.1)),length(rho),length(rho))
# contour(rho, rho, sm, add=T,levels=c(0.008,0.01,0.012))
# 
# image(rho, rho, Eg.mat, xlab="Breeding synchrony", ylab="Overwintering synchrony", asp=1, main="main Eg",
#       col=pal(50), zlim=c(-.015,.015))
# tmpdf<-data.frame(z=c(Eg.mat), x=expand.grid(rho,rho)[,1], y=expand.grid(rho,rho)[,2])
# sm<-matrix(predict(loess(z~x+y, data=tmpdf, span=0.1)),length(rho),length(rho))
# contour(rho, rho, sm, add=T, levels=c(0,0.001,0.002,0.003))
# 
# #alternate model
# image(rho, rho, Ntcor.mat.alt, xlab="Breeding synchrony", ylab="Overwintering synchrony", asp=1, main="alt cor(Nt)",
#       col=pal(50), zlim=c(-1,1))
# tmpdf<-data.frame(z=c(Ntcor.mat.alt), x=expand.grid(rho,rho)[,1], y=expand.grid(rho,rho)[,2])
# sm<-matrix(predict(loess(z~x+y, data=tmpdf, span=0.1)),length(rho),length(rho))
# contour(rho, rho, sm, add=T)
# 
# image(rho, rho, El.mat.alt, xlab="Breeding synchrony", ylab="Overwintering synchrony", asp=1, main="alt El",
#       col=pal(50), zlim=c(-.11,.11))
# tmpdf<-data.frame(z=c(El.mat.alt), x=expand.grid(rho,rho)[,1], y=expand.grid(rho,rho)[,2])
# sm<-matrix(predict(loess(z~x+y, data=tmpdf, span=0.1)),length(rho),length(rho))
# contour(rho, rho, sm, add=T, levels=c(0.04,0.05))
# 
# image(rho, rho, Eg.mat.alt, xlab="Breeding synchrony", ylab="Overwintering synchrony", asp=1, main="alt Eg",
#       col=pal(50), zlim=c(-.02,.02))
# tmpdf<-data.frame(z=c(Eg.mat.alt), x=expand.grid(rho,rho)[,1], y=expand.grid(rho,rho)[,2])
# sm<-matrix(predict(loess(z~x+y, data=tmpdf, span=0.1)),length(rho),length(rho))
# contour(rho, rho, sm, add=T, nlevels = 5)
# 
# #difference
# image(rho, rho, diff.Ntcor, xlab="Breeding synchrony", ylab="Overwintering synchrony", asp=1, main="diff cor(Nt)",
#       col=pal(50), zlim=c(-.3,.3))
# tmpdf<-data.frame(z=c(diff.Ntcor), x=expand.grid(rho,rho)[,1], y=expand.grid(rho,rho)[,2])
# sm<-matrix(predict(loess(z~x+y, data=tmpdf, span=0.1)),length(rho),length(rho))
# contour(rho, rho, sm, add=T)
# 
# image(rho, rho, diff.El, xlab="Breeding synchrony", ylab="Overwintering synchrony", asp=1, main="diff El",
#       col=pal(50), zlim=c(-.11,.11))
# tmpdf<-data.frame(z=c(diff.El), x=expand.grid(rho,rho)[,1], y=expand.grid(rho,rho)[,2])
# sm<-matrix(predict(loess(z~x+y, data=tmpdf, span=0.1)),length(rho),length(rho))
# contour(rho, rho, sm, add=T, levels=c(-0.08,-0.06,-0.04,-0.02,0))
# 
# image(rho, rho, diff.Eg, xlab="Breeding synchrony", ylab="Overwintering synchrony", asp=1, main="diff Eg",
#       col=pal(50), zlim=c(-.015,.015))
# tmpdf<-data.frame(z=c(diff.Eg), x=expand.grid(rho,rho)[,1], y=expand.grid(rho,rho)[,2])
# sm<-matrix(predict(loess(z~x+y, data=tmpdf, span=0.1)),length(rho),length(rho))
# contour(rho, rho, sm, add=T, levels=c(-0.007,-0.006,-0.005,-0.004))
# 
# dev.off()
# 
# 
# tiff(paste0("~/Box Sync/SynchronyLifestageModel/plotoutput/compare_vs_basic_multnoise",scentxt,".tif"), units="in", res=300, width=6.5, height=6.5)
# 
# par(mfcol=c(3,3), mar=c(4,4,1.5,1), mgp=c(2.7,1,0), tcl=-0.4)
# #main model
# image(rho, rho, Ntcor.mat, xlab="Breeding synchrony", ylab="Overwintering synchrony", asp=1, main="main cor(Nt)",
#       col=pal(50), zlim=c(-1,1))
# tmpdf<-data.frame(z=c(Ntcor.mat), x=expand.grid(rho,rho)[,1], y=expand.grid(rho,rho)[,2])
# sm<-matrix(predict(loess(z~x+y, data=tmpdf, span=0.1)),length(rho),length(rho))
# contour(rho, rho, sm, add=T)
# 
# image(rho, rho, El.mat, xlab="Breeding synchrony", ylab="Overwintering synchrony", asp=1, main="main El",
#       col=pal(50), zlim=c(-.11,.11))
# tmpdf<-data.frame(z=c(El.mat), x=expand.grid(rho,rho)[,1], y=expand.grid(rho,rho)[,2])
# sm<-matrix(predict(loess(z~x+y, data=tmpdf, span=0.1)),length(rho),length(rho))
# contour(rho, rho, sm, add=T,levels=c(0.008,0.01,0.012))
# 
# image(rho, rho, Eg.mat, xlab="Breeding synchrony", ylab="Overwintering synchrony", asp=1, main="main Eg",
#       col=pal(50), zlim=c(-.015,.015))
# tmpdf<-data.frame(z=c(Eg.mat), x=expand.grid(rho,rho)[,1], y=expand.grid(rho,rho)[,2])
# sm<-matrix(predict(loess(z~x+y, data=tmpdf, span=0.1)),length(rho),length(rho))
# contour(rho, rho, sm, add=T, levels=c(0,0.001,0.002,0.003))
# 
# #alternate model
# image(rho, rho, Ntcor.mat.br, xlab="Breeding synchrony", ylab="Overwintering synchrony", asp=1, main="basic cor(Nt)",
#       col=pal(50), zlim=c(-1,1))
# tmpdf<-data.frame(z=c(Ntcor.mat.br), x=expand.grid(rho,rho)[,1], y=expand.grid(rho,rho)[,2])
# sm<-matrix(predict(loess(z~x+y, data=tmpdf, span=0.1)),length(rho),length(rho))
# contour(rho, rho, sm, add=T)
# 
# image(rho, rho, El.mat.br, xlab="Breeding synchrony", ylab="Overwintering synchrony", asp=1, main="basic El",
#       col=NA, zlim=c(-.25,.25))
# tmpdf<-data.frame(z=c(El.mat.br), x=expand.grid(rho,rho)[,1], y=expand.grid(rho,rho)[,2])
# sm<-matrix(predict(loess(z~x+y, data=tmpdf, span=0.1)),length(rho),length(rho))
# text(0.5,0.5,"No local\nextinctions")
# 
# image(rho, rho, Eg.mat.br, xlab="Breeding synchrony", ylab="Overwintering synchrony", asp=1, main="basic Eg",
#       col=NA, zlim=c(-.02,.02))
# tmpdf<-data.frame(z=c(Eg.mat.br), x=expand.grid(rho,rho)[,1], y=expand.grid(rho,rho)[,2])
# sm<-matrix(predict(loess(z~x+y, data=tmpdf, span=0.1)),length(rho),length(rho))
# text(0.5,0.5,"No local\nextinctions")
# 
# #difference
# image(rho, rho, diff2.Ntcor, xlab="Breeding synchrony", ylab="Overwintering synchrony", asp=1, main="diff2 cor(Nt)",
#       col=pal(50), zlim=c(-.7,.7))
# tmpdf<-data.frame(z=c(diff2.Ntcor), x=expand.grid(rho,rho)[,1], y=expand.grid(rho,rho)[,2])
# sm<-matrix(predict(loess(z~x+y, data=tmpdf, span=0.1)),length(rho),length(rho))
# contour(rho, rho, sm, add=T)
# 
# image(rho, rho, diff2.El, xlab="Breeding synchrony", ylab="Overwintering synchrony", asp=1, main="diff2 El",
#       col=pal(50), zlim=c(-.15,.15))
# tmpdf<-data.frame(z=c(diff2.El), x=expand.grid(rho,rho)[,1], y=expand.grid(rho,rho)[,2])
# sm<-matrix(predict(loess(z~x+y, data=tmpdf, span=0.1)),length(rho),length(rho))
# contour(rho, rho, sm, add=T,levels=c(0.008,0.01,0.012))
# 
# image(rho, rho, diff2.Eg, xlab="Breeding synchrony", ylab="Overwintering synchrony", asp=1, main="diff2 Eg",
#       col=pal(50), zlim=c(-.015,.015))
# tmpdf<-data.frame(z=c(diff2.Eg), x=expand.grid(rho,rho)[,1], y=expand.grid(rho,rho)[,2])
# sm<-matrix(predict(loess(z~x+y, data=tmpdf, span=0.1)),length(rho),length(rho))
# contour(rho, rho, sm, add=T, levels=c(0,0.001,0.002,0.003))
# 
# dev.off()

png(paste0("~/Box Sync/SynchronyLifestageModel/plotoutput/fig5_comparison_multnoise_",scentxt,".png"), units="in", res=300, width=6, height=6.55)

par(mfcol=c(3,3), mar=c(2,2,2.5,1), oma=c(1.5,1.5,0,0),mgp=c(2,0.6,0), tcl=-0.4)
#main model
image(rho, rho, Ntcor.mat, xlab="", ylab="", asp=1, 
      main="", col=pal(50), zlim=c(-1,1))
tmpdf<-data.frame(z=c(Ntcor.mat), x=expand.grid(rho,rho)[,1], y=expand.grid(rho,rho)[,2])
sm<-matrix(predict(loess(z~x+y, data=tmpdf, span=0.1)),length(rho),length(rho))
contour(rho, rho, sm, add=T)
mtext("Main model",3,line=0.1,cex=0.7)
text(0.05,0.95,"a)")

image(rho, rho, El.mat, xlab="", ylab="", asp=1, 
      main="", col=pal(50), zlim=c(-.05,.05))
tmpdf<-data.frame(z=c(El.mat), x=expand.grid(rho,rho)[,1], y=expand.grid(rho,rho)[,2])
sm<-matrix(predict(loess(z~x+y, data=tmpdf, span=0.1)),length(rho),length(rho))
contour(rho, rho, sm, add=T,levels=c(0.008,0.01,0.012))
mtext("Main model",3,line=0.1, cex=0.7)
text(0.05,0.95,"d)")

image(rho, rho, Eg.mat, xlab="", ylab="", asp=1, 
      main="",
      col=pal(50), zlim=c(-.01,.01))
tmpdf<-data.frame(z=c(Eg.mat), x=expand.grid(rho,rho)[,1], y=expand.grid(rho,rho)[,2])
sm<-matrix(predict(loess(z~x+y, data=tmpdf, span=0.1)),length(rho),length(rho))
contour(rho, rho, sm, add=T, levels=c(0,0.001,0.002,0.003))
mtext("Main model",3,line=0.1, cex=0.7)
text(0.05,0.95,"g)")

#difference - basic ricker
image(rho, rho, diff2.Ntcor, xlab="", ylab="", asp=1, main="",
      col=pal(50), zlim=c(-.7,.7))
tmpdf<-data.frame(z=c(diff2.Ntcor), x=expand.grid(rho,rho)[,1], y=expand.grid(rho,rho)[,2])
sm<-matrix(predict(loess(z~x+y, data=tmpdf, span=0.1)),length(rho),length(rho))
contour(rho, rho, sm, add=T)
mtext("Difference: alternate 1",3,line=0.1,cex=0.7)
mtext("Population spatial synchrony",3,line=1.1,cex=0.9)
text(0.05,0.95,"b)")

image(rho, rho, diff2.El, xlab="", ylab="", asp=1, main="",
      col=pal(50), zlim=c(-.05,.05))
tmpdf<-data.frame(z=c(diff2.El), x=expand.grid(rho,rho)[,1], y=expand.grid(rho,rho)[,2])
sm<-matrix(predict(loess(z~x+y, data=tmpdf, span=0.1)),length(rho),length(rho))
contour(rho, rho, sm, add=T,levels=c(0.008,0.01,0.012))
mtext("Difference: alternate 1",3,line=0.1,cex=0.7)
mtext("Local extinction rate",3,line=1.1,cex=0.9)
text(0.05,0.95,"e)")

image(rho, rho, diff2.Eg, xlab="", ylab="", asp=1, main="",
      col=pal(50), zlim=c(-.01,.01))
tmpdf<-data.frame(z=c(diff2.Eg), x=expand.grid(rho,rho)[,1], y=expand.grid(rho,rho)[,2])
sm<-matrix(predict(loess(z~x+y, data=tmpdf, span=0.1)),length(rho),length(rho))
contour(rho, rho, sm, add=T, levels=c(0,0.001,0.002,0.003))
mtext("Difference: alternate 1",3,line=0.1,cex=0.7)
mtext("Global extinction rate",3,line=1.1,cex=0.9)
text(0.05,0.95,"h)")

#difference - alternate seasonal model
image(rho, rho, diff.Ntcor, xlab="", ylab="", asp=1, main="",
      col=pal(50), zlim=c(-.2,.2))
tmpdf<-data.frame(z=c(diff.Ntcor), x=expand.grid(rho,rho)[,1], y=expand.grid(rho,rho)[,2])
sm<-matrix(predict(loess(z~x+y, data=tmpdf, span=0.1)),length(rho),length(rho))
contour(rho, rho, sm, add=T)
mtext("Difference: alternate 2",3,line=0.1,cex=0.7)
text(0.05,0.95,"c)")

image(rho, rho, diff.El, xlab="", ylab="", asp=1, main="",
      col=pal(50), zlim=c(-.1,.1))
tmpdf<-data.frame(z=c(diff.El), x=expand.grid(rho,rho)[,1], y=expand.grid(rho,rho)[,2])
sm<-matrix(predict(loess(z~x+y, data=tmpdf, span=0.1)),length(rho),length(rho))
contour(rho, rho, sm, add=T, levels=c(-0.08,-0.06,-0.04,-0.02,0))
mtext("Difference: alternate 2",3,line=0.1,cex=0.7)
text(0.05,0.95,"f)")

image(rho, rho, diff.Eg, xlab="", ylab="", asp=1, main="",
      col=pal(50), zlim=c(-.01,.01))
tmpdf<-data.frame(z=c(diff.Eg), x=expand.grid(rho,rho)[,1], y=expand.grid(rho,rho)[,2])
sm<-matrix(predict(loess(z~x+y, data=tmpdf, span=0.1)),length(rho),length(rho))
contour(rho, rho, sm, add=T, levels=c(-0.007,-0.006,-0.005,-0.004))
mtext("Difference: alternate 2",3,line=0.1,cex=0.7)
text(0.05,0.95,"i)")

mtext("Spatial synchrony of breeding season environment",1,outer=T,cex=0.9)
mtext("Spatial synchrony of overwintering season environment",2,outer=T,cex=0.9)

dev.off()

```
